### 2018-02-05 master/paper.tex
Add a TLSF evaluation

% Title
\thispagestyle{empty}
\begin{center}
\vspace*{5mm}
{\Huge {\bf Master's Thesis}}\\
\vspace{2cm}
% {\Large 題\hspace{8mm}目}\\
% \vspace{1cm}
\underline{\LARGE{Component-Based Software Development Framework}} \\
\vspace{0.5cm}
\underline{\LARGE{for Embedded IoT Devices}} \\
\vspace{12mm}
{\large Supervisor}\\
\vspace{6mm}
\underline{\Large Professor Toshimitsu Ushio}\\
　\\
\underline{\Large Assistant Professor Takuya Azumi}\\
\vspace{8mm}
{\large By}\\
\vspace{6mm}
\underline{\Large Takuro Yamamoto}\\
\vspace{10mm}
{\Large February 7, 2018}\\
\vspace{14mm}
{\Large Division of Mathematical Science for Social Systems,\\Department of Systems Innovation,\\Graduate School of Engineering Science, Osaka University}\\
\end{center}
\clearpage
\setcounter{page}{0}
\pagenumbering{roman}

@@

Fig. \ref{fig:EvaluationOfTLSFStatistics} shows the memory usage of a RiteVM acquired by statistical information of TLSF+TECS.
When the RiteVM is activated, a large memory is allocated and the initialization is performed for several seconds.
After that, the application is running for about 20 seconds and the RiteVM is terminated.
The reduction in memory usage at regular time intervals is due to the GC function of RiteVM.
TLSF+TECS can visualize the behavior of GC and help to verify its operation.
Furthermore, when the RiteVM is terminated, the memory used by RiteVM is not completely released and a little used memory (a few kilobytes) remains.
This remaining memory causes a memory leak when the number of RiteVMs increases or a RiteVM repeats activation and shutdown.
In this way, it is useful for finding bugs related to memory, which is hard to find.

\begin{figure}[t]
    \centering
    \includegraphics[width=12cm,clip]{figure/EvaluationOfTLSFStatistics.pdf}
    \caption{Memory usage of RiteVM (mruby VM) by TLSFStatistics component}
    \label{fig:EvaluationOfTLSFStatistics}
\end{figure}

@@

This paper presented an component-based framework that can develop software including network applications for embedded IoT devices using a scripting language.
It is an extended framework of mruby on TECS, including TINET+TECS and TLSF+TECS.
In the proposed framework, mruby programs can call TINET+TECS functions through the mruby-TECS bridge.
Development of software for IoT devices such as sensors and actuators will be more efficient due to the high productivity of mruby.

@@

%Publication List
\chapter*{Publication List}
\addcontentsline{toc}{chapter}{Publication List}
\section*{Journal}
\begin{enumerate}[{[}1{]}]
\item
    Takuro Yamamoto, Takuma Hara, Takuya Ishikawa, Hiroshi Oyama, Hiroaki Takada, and Takuya Azumi,
    ``Component-Based mruby Platform for IoT Devices,"
    \emph{IPSJ Journal of Information Processing},
    2018 (submitted).
\item
    Takuro Yamamoto, Hiroshi Oyama, and Takuya Azumi,
    ``Component-Based Framework of Lightweight Ruby for Efficient Embedded Software Development,''
    \emph{JSSST Journal on Computer Software},
    vol. 34, no. 4, pp. 3-16, 2017.
\end{enumerate}

>>>>

% Title
\thispagestyle{empty}
\begin{center}
\vspace*{5mm}
{\Huge {\bf Master's Thesis}}\\
\vspace{2cm}
% {\Large 題\hspace{8mm}目}\\
% \vspace{1cm}
\underline{\LARGE{Component-Based Software Development Framework}} \\
\vspace{0.5cm}
\underline{\LARGE{for Embedded IoT Devices}} \\
\vspace{12mm}
{\large Supervisor}\\
\vspace{6mm}
\underline{\Large Professor Toshimitsu Ushio}\\
　\\
\underline{\Large Assistant Professor Takuya Azumi}\\
\vspace{8mm}
{\large By}\\
\vspace{6mm}
\underline{\Large Takuro Yamamoto}\\
\vspace{10mm}
{\Large February 2, 2018}\\
\vspace{14mm}
{\Large Division of Mathematical Science for Social Systems,}\\
{\Large Department of Systems Innovation,}\\
{\Large Graduate School of Engineering Science, Osaka University}\\
\end{center}
\clearpage
\setcounter{page}{0}
\pagenumbering{roman}

@@

{\bf Memory usage:}
Fig. \ref{fig:EvaluationOfTLSFStatistics} shows the memory usage of a RiteVM acquired by statistical information of TLSF+TECS.
When the RiteVM is activated, a large memory is allocated and the initialization is performed for several seconds.
After that, the application is running for about 20 seconds and the RiteVM is terminated.
The reduction in memory usage at regular time intervals is due to the GC function of RiteVM.
TLSF+TECS can visualize the behavior of GC and help to verify its operation.
Furthermore, when the RiteVM is terminated, the memory used by RiteVM is not completely released and a little used memory (a few kilobytes) remains.
This remaining memory causes a memory leak when the number of RiteVMs increases or a RiteVM repeats activation and shutdown.
In this way, it is useful for finding bugs related to memory, which is hard to find.

\begin{figure}[t]
    \centering
    \includegraphics[width=11cm,clip]{figure/EvaluationOfTLSFStatistics.pdf}
    \caption{Memory usage of RiteVM (mruby VM) by TLSFStatistics component}
    \label{fig:EvaluationOfTLSFStatistics}
\end{figure}

{\bf Memory frequency:}
Fig. \ref{fig:EvaluationOfTLSFFrequency} evaluates how much memory size and how often a RiteVM requests.
In this evaluation, the same application as Fig. \ref{fig:EvaluationOfTLSFStatistics} runs for about 30 seconds.
During 30 seconds, the RiteVM requests {\it malloc} quite frequency.
In the case of designating heap areas with fixed-size memory, it is necessary to property configure memory blocks suitable for an application.
For example, 10 blocks of 64 bytes, 20 blocks of 128 bytes, and 3 blocks of 64 kilobytes.
In particular, it is not easy to analyze how many memory blocks are needed with RiteVMs, which consumes memory considerably with a high frequency.
With TLSF+TECS, you only need to prepare a large heap area; therefore, such a workload and useless memory are eliminated.

\begin{figure}[t]
    \centering
    \includegraphics[width=11cm,clip]{figure/EvaluationOfTLSFFrequency.pdf}
    \caption{Memory frequency of RiteVM (mruby VM) by TLSFStatistics component}
    \label{fig:EvaluationOfTLSFFrequency}
\end{figure}

@@

This paper presented a component-based framework that can develop software including network applications for embedded IoT devices using a scripting language.
It is an extended framework of mruby on TECS, including TINET+TECS and TLSF+TECS.
In the proposed framework, mruby programs can call TINET+TECS functions through the mruby-TECS bridge.
Development of software for IoT devices such as sensors and actuators will be more efficient due to the high productivity of mruby.

@@

%Publication List
\chapter*{Publication List}
\addcontentsline{toc}{chapter}{Publication List}
\section*{Journal}
\begin{enumerate}[{[}1{]}]
\item
    Takuro Yamamoto, Takuma Hara, Takuya Ishikawa, Hiroshi Oyama, Hiroaki Takada, and Takuya Azumi,
    ``Component-Based mruby Platform for IoT Devices,"
    \emph{IPSJ Journal of Information Processing},
    2018 (conditionally accepted).
\item
    Takuro Yamamoto, Hiroshi Oyama, and Takuya Azumi,
    ``Component-Based Framework of Lightweight Ruby for Efficient Embedded Software Development,''
    \emph{JSSST Journal on Computer Software},
    vol. 34, no. 4, pp. 3-16, 2017.
\end{enumerate}
